Paper_analyses

### 2021-08-04 Paper_Analyses_subj_obje_arousal.Rmd
Update Paper_Analyses_subj_obje_arousal.Rmd

plots_paper$interaction_ar_vl+p$graphstyle
```
interaction plot

@@

#  let's use the order arousal, valence, arousal x valence brightness
plots_timecourse$eff_size_pup_amp <-   timecourse_60bin_result_df %>% 
  select("timebins","Estimate_ar", "Estimate_vl", "Estimate_br", "Estimate_ar_vl") %>% 
  pivot_longer(-timebins, names_to = "variable", values_to = "Estimate")%>%
    subset(!is.na(Estimate))%>%
  #change the order of the coloring variable here and the name of legends
  mutate(variable = factor(variable, c("Estimate_ar", "Estimate_vl","Estimate_ar_vl",  "Estimate_br"), labels = c("arousal", "valence", "arousal x valence", "brightness")))%>%
  ggplot(aes(timebins, Estimate, group = variable, color= variable))+
  geom_line(aes(linetype = variable), size = 1)+

@@

plots_timecourse$eff_size_pup_amp

@@

use the same dataas timecourse to plot aggregated analyses
aggregate arousal plot
```{r}

@@

>>>>

plots_paper$interaction_ar_vl+p$graphstyle

plots_paper$interaction_ar_vl
```
interaction plot

@@

#  let's use the order arousal, valence, arousal x valence brightness
View(timecourse_60bin_result_df)
plots_timecourse$eff_size_pup_amp <-   timecourse_60bin_result_df[1:56,] %>% 
  select("timebins","Estimate_ar", "Estimate_vl", "Estimate_br", "Estimate_ar_vl") %>% 
  pivot_longer(-timebins, names_to = "variable", values_to = "Estimate")%>%
    subset(!is.na(Estimate))%>%
  #change the order of the coloring variable here and the name of legends
  mutate(variable = factor(variable, c("Estimate_ar", "Estimate_vl","Estimate_ar_vl",  "Estimate_br"), labels = c("arousal", "valence", "arousal x valence", "brightness")))%>%
  ggplot(aes(timebins, Estimate, group = variable, color= variable))+
  geom_line(aes(linetype = variable), size = 1)+

@@

plots_timecourse$eff_size_pup_amp
plots_timecourse$eff_size_pup_velocity

@@

use the same datas timecourse to plot aggregated analyses
aggregate arousal plot
```{r}

@@

plots_paper$interaction_ar_vl

# correlation plot

plots_paper$pupil_correlation <-   db_full4new_stim_screen_pupil_nopract %>%
    subset(ssid_num<500)%>%
  subset(pupil_outlier == FALSE & arousal_outler == FALSE)%>%
   group_by(ssid,Alexithymia, mediansplit_ground_valence)%>%
    mutate(cortest = cor.test(arousal_c, pup_basCor)$estimate)%>%
   group_by(ssid,Alexithymia, mediansplit_ground_valence)%>%
    summarise_if(is.numeric, mean, na.rm = TRUE)%>%
     ggplot(aes(mediansplit_ground_valence, cortest, fill = mediansplit_ground_valence))+
     geom_bar(stat="summary", fun.y = "mean", alpha = .5)+
     geom_jitter(width = .1, alpha = .1)+
        stat_summary( geom = 'pointrange')+
        stat_summary(aes(group = ssid), geom = 'line', alpha = .1)+
    ylab("R sujective vs pupil arousal")+
     scale_fill_brewer(palette = "Dark2")+
     p$graphstyle+
     theme(axis.title.x = element_blank())

plots_paper$pupil_correlation

# timecourse plot pupil
